An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps

### 2020-01-12 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
suggestions on paper to finish it, see XXX

The current practice for presenting geogspatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties. The units are filled with colour to represent the value of the statistic \citep{EI}.

@@

The following code creates a map for all the Statistical Areas at Level 2 in Tasmania:

```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE}

# install.packages("sugarbag")
library(sugarbag)

# Create hexagon location grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.2,
    buffer_dist = 1.2)

# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "SA2_NAME16",
  # same column used in create_centroids
  hex_size = 0.2,
  # same size used in create_grid
  hex_filter = 10,
  use_neighbours = tas_sa2,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE)
```

@@

# Australian Cancer Atlas

@@

@@

@@

@@

>>>>

The current practice for presenting geospatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties. The units are filled with colour to represent the value of the statistic \citep{EI}.

@@

@@

## Installation

The package can be installed from CRAN:

```{r eval=FALSE}
install.packages("sugarbag")
```

and the development version can be install from the GitHub repository:

```{r eval=FALSE}
devtools::install_github("srkobakian","sugarbag")
```

Load the library into your R session with:

```{r eval=FALSE}
library(sugarbag)
```

## Creating a hexagon tile map

The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.

```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
# Load data
data(tas_sa2)

# Create hexagon grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.2,
    buffer_dist = 1.2)

# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "SA2_NAME16",
  # same column used in create_centroids
  hex_size = 0.2,
  # same size used in create_grid
  hex_filter = 10,
  use_neighbours = tas_sa2,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE)

# Prepare to plot
fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)

# Make a plot
library(ggplot2)
ggplot(fort_hex) + 
  geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
  scale_fill_distiller("", palette="PRGn")
```

# Applications

## Australian Cancer Atlas

XXX Show whole Australia male liver cancer with choropleth and hexagon tile map, and discuss the pros/cons of the result, for understanding the incidence.

@@

XXX Move this image (ref: sir) to the end of the algorithm section to illustrate the final result for Tassie

@@

## Election results

XXX Code from web site, and a couple of paragraphs of explanation

# Animation

XXX show how to make an animation, and make a link to a web page where the animation can be viewed

@@

Structure of conclusions: (1) summarise paper, discuss limitations, suggest future directions

@@

# Acknowledgements

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations. They would also like to thank Professor Kerrie Mengersen and Dr Earl Duncan for suggestions and comments. Mitch O'Hara-Wild provided assistance with some parts of the algorithm and code. Sayani Gupta provided helpful advice on parts of this paper.

The code for sugarbag can be found at XXX, along with details on installation and usage.

### 2020-01-12 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
suggestions on paper to finish it, see XXX

\hypertarget{tasmania}{%
\subsection{Tasmania}\label{tasmania}}

@@

The following code creates a map for all the Statistical Areas at Level
2 in Tasmania:

\begin{CodeInput}
R> # install.packages("sugarbag")
R> library(sugarbag)
R> 
R> # Create centroids set
R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
R> 
R> # Create hexagon location grid
R> grid <- create_grid(centroids = centroids,
R+     hex_size = 0.2,
R+     buffer_dist = 1.2)
R> 
R> # Allocate polygon centroids to hexagon grid points
R> hex_allocated <- allocate(
R+   centroids = centroids,
R+   hex_grid = grid,
R+   sf_id = "SA2_NAME16",
R+   # same column used in create_centroids
R+   hex_size = 0.2,
R+   # same size used in create_grid
R+   hex_filter = 10,
R+   use_neighbours = tas_sa2,
R+   focal_points = capital_cities %>% filter(points == "Hobart"),
R+   width = 35,
R+   verbose = FALSE)
\end{CodeInput}
\end{CodeChunk}

@@

\hypertarget{australian-cancer-atlas}{%
\section{Australian Cancer Atlas}\label{australian-cancer-atlas}}

@@

@@

>>>>

\hypertarget{polygon-set}{%
\subsection{Polygon set}\label{polygon-set}}

@@

@@

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

The package can be installed from CRAN:

\begin{CodeInput}
R> install.packages("sugarbag")
\end{CodeInput}
\end{CodeChunk}

and the development version can be install from the GitHub repository:

\begin{CodeInput}
R> devtools::install_github("srkobakian","sugarbag")
\end{CodeInput}
\end{CodeChunk}

Load the library into your R session with:

\begin{CodeInput}
R> library(sugarbag)
\end{CodeInput}
\end{CodeChunk}

\hypertarget{creating-a-hexagon-tile-map}{%
\subsection{Creating a hexagon tile
map}\label{creating-a-hexagon-tile-map}}

The following code creates the hexagon tile map for all the Statistical
Areas at Level 2 in Tasmania.

\begin{CodeInput}
R> # Load data
R> data(tas_sa2)
R> 
R> # Create centroids set
R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
R> 
R> # Create hexagon grid
R> grid <- create_grid(centroids = centroids,
R>     hex_size = 0.2,
R>     buffer_dist = 1.2)
R> 
R> # Allocate polygon centroids to hexagon grid points
R> hex_allocated <- allocate(
R>   centroids = centroids,
R>   hex_grid = grid,
R>   sf_id = "SA2_NAME16",
R>   # same column used in create_centroids
R>   hex_size = 0.2,
R>   # same size used in create_grid
R>   hex_filter = 10,
R>   use_neighbours = tas_sa2,
R>   focal_points = capital_cities %>% filter(points == "Hobart"),
R>   width = 35,
R>   verbose = FALSE)
R> 
R> # Prepare to plot
R> fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
R> 
R> # Make a plot
R> library(ggplot2)
R> ggplot(fort_hex) + 
R>   geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
R>   scale_fill_distiller("", palette="PRGn")
\end{CodeInput}
\end{CodeChunk}

\hypertarget{applications}{%
\section{Applications}\label{applications}}

\hypertarget{australian-cancer-atlas}{%
\subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}

XXX Show whole Australia male liver cancer with choropleth and hexagon
tile map, and discuss the pros/cons of the result, for understanding the
incidence.

@@

\hypertarget{election-results}{%
\subsection{Election results}\label{election-results}}

XXX Code from web site, and a couple of paragraphs of explanation

\hypertarget{animation}{%
\section{Animation}\label{animation}}

XXX show how to make an animation, and make a link to a web page where
the animation can be viewed

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

The authors would like to thank the Australian Cancer Atlas team for
discussions regarding alternative spatial visualizations. They would
also like to thank Professor Kerrie Mengersen and Dr Earl Duncan for
suggestions and comments. Mitch O'Hara-Wild provided assistance with
some parts of the algorithm and code. Sayani Gupta provided helpful
advice on parts of this paper.

The code for sugarbag can be found at XXX, along with details on
installation and usage.
